[dcpo_demsupport]

### 2020-08-05 paper/dcpo_demsupport.Rmd
add data/dcpo_sigma.rda and include sigma in model 1.  Closes #8

@@

@@

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset)
})

@@

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

>>>>

intro

More data, better method, superior measure

review models

results

@@

dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")

save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))

@@

reformat_dcpo_output <- function(x, parameter_name) {
  df_temp <- x %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = parameter_name) %>%
    arrange(country, year)
  return(df_temp)
}

df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_dcpo, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
             plm::lag(sigma, 1) + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset)
})

@@

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(sigma, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
